Supporting information: Tail associations and their impact on extinction risk

### 2019-10-30 SuppMat.Rmd
table 1, second column heading fixed

dt2<-tibble("Density dependence $(\\lambda_i(t))$ with noise $(\\epsilon_i(t))$" = c("$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} \\exp[r (1-P_i(t)/K)$]",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/(1+aP_i(t))^b$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/[1+(aP_i(t))^b]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/[1+\\exp \\{-a(1-P_i(t)/b)\\}]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} [1+r(1-P_i(t)/K)]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} [1+r(K-P_i(t))\\{1-\\exp(-sP_i(t))\\}]$"
))

>>>>

dt2<-tibble("$\\lambda_i(t)$" = c("$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} \\exp[r (1-P_i(t)/K)$]",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/(1+aP_i(t))^b$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/[1+(aP_i(t))^b]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} r/[1+\\exp \\{-a(1-P_i(t)/b)\\}]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} [1+r(1-P_i(t)/K)]$",
                          "$\\exp(\\epsilon_i(t)) \\hspace{0.1 cm} [1+r(K-P_i(t))\\{1-\\exp(-sP_i(t))\\}]$"
))
